Graph Topology Learning from Binary Signals on Graph

### 2022-04-30 poster html copy/poster html.Rmd
GSP Regressor Results.

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
  - name: Jing Guo
affiliation:
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
logoright_name: pictures/DSI_Hexbin_sticker_01.png
logoleft_name: pictures/logo1.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

@@

 <body>      
        <p style="color:black;font-size:32px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Robin Donatello for approving this work for Data Science Capstone Project.</p>    
</body>

>>>>

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
  - name: Dr. Jing Guo, Ph.D.
affiliation:
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
logoright_name: pictures/DSI_Hexbin_sticker_01.png
logoleft_name: pictures/logo1.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

@@

 <body>      
        <p style="color:black;font-size:32px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Dr. Robin Donatello, Ph.D., for approving this work for Data Science Capstone Project.</p>    
</body>
